Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex

This is a testcase original from the \jsc{} suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, but this test uses a long integer
instead. As result, the engine crashes. The team answered that this
was an incompatibility by design as the function was not expected to
receive such a long value.

>>>>

This is a testcase original from the \jsc{} suite that the
\radamsa\ fuzzer modified. Instead of the long integer passed as
argument to \CodeIn{"foo".repeat()}, the original test used the
integer literal 3. The engine crashes on this input as result. The
team answered that this was an incompatibility by design as the
function repeat was not expected to receive such a long value.
